---
title: "Introduction to OmniAgeRData"
author:
- name: Zhaozhen Du
  affiliation: Shanghai Institute of Nutrition and Health, CAS
  email: duzhaozhen2022@sinh.ac.cn
- name: Andrew E. Teschendorff
  affiliation: Shanghai Institute of Nutrition and Health, CAS
  email: andrew@sinh.ac.cn
package: OmniAgeRData
output: 
  BiocStyle::html_document:
    toc_float: true
vignette: |
  %\VignetteIndexEntry{Introduction to OmniAgeRData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This package provides aging omic biomarker model parameters and example data for
the `OmniAgeR` package. It utilizes `ExperimentHub` to deliver both traditional 
clock coefficients and large-scale synthetic datasets.

## Installation

```{r install-bioc, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install(c("OmniAgeRData"))
```

# Exploring Available Resources
You can explore all available OmniAgeR datasets and models 
through ExperimentHub:

```{r explore, eval=TRUE}
library(OmniAgeRData)
library(ExperimentHub)

eh <- ExperimentHub()
query(eh, "OmniAgeRData")
```


During package review or development, the development versions can be installed from GitHub:

```{r install-github, eval=FALSE}
if (!requireNamespace("remotes", quietly = TRUE))
    install.packages("remotes")

remotes::install_github("Duzhaozhen/OmniAgeRData")
```

# Data Retrieval
The recommended way to load data is using our wrapper function getOmniAgeRData().

```{r retrieve, eval=TRUE}
lung_data <- getOmniAgeRData("omniager_lung_inv.rds")
head(lung_data)
```

# Session Information
```{r sessionInfo, eval=TRUE}
sessionInfo()
```

